%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry
{Customizable digital library system as a complement university libraries.} % Role
{ISSN 2307-2113 } % Event
{} % Location
{} % Date(s)
{ % Description(s)
}

\cventry
{Multimedia content and virtual reality technologies for development WAP} % Role
{IV International Congress of technologies} % Event
{} % Location
{2009} % Date(s)
{ % Description(s)
}

\cventry
{Customizing content management system Drupal} % Role
{II computer symposium and community} % Event
{} % Location
{2009} % Date(s)
{ % Description(s)
}

\cventry
{Customizable digital library.} % Role
{XIV International Congress of Informatics in Education} % Event
{} % Location
{2011} % Date(s)
{ % Description(s)
}

\cventry
{The LAMP architecture for libraries, journals and document repositories} % Role
{XV Congress of computers in education} % Event
{} % Location
{2013} % Date(s)
{ % Description(s)
}

\cventry
{Theme Use and application development and innovations in open source standards, development of a digital library using the Drupal CMS} % Role
{10th week of FORDES technology } % Event
{} % Location
{2010} % Date(s)
{ % Description(s)
}

\cventry
{Theme The use of ICT in the formation of human capital, alternative development for Firefox.} % Role
{10th week of FORDES technology } % Event
{} % Location
{2010} % Date(s)
{ % Description(s)
}

\cventry
{Digital Library as a complement to university libraries, at the grassroots level.} % Role
{10. University 2012} % Event
{} % Location
{2011} % Date(s)
{ % Description(s)
}

\cventry
{IX International Workshop on business intelligence and knowledge management in the company, Proposal for a Digital Library} % Role
{11. Info 2012} % Event
{} % Location
{2012} % Date(s)
{ % Description(s)
}

\cventry
{Digital library: a complement to the system of university libraries.} % Role
{Congress Ibero-American education and society (CIEDUC'2013)} % Event
{} % Location
{2013} % Date(s)
{ % Description(s)
}

\cventry
{III informational workshop for industry software and web applications for information management, WAP technologies for design development.} % Role
{Uciencia 2008} % Event
{} % Location
{2008} % Date(s)
{ % Description(s)
}

\cventry
{Technologies for WAP development.} % Role
{Uciencia 2009} % Event
{} % Location
{2009} % Date(s)
{ % Description(s)
}

\cventry
{I workshop systems information management information and The knowledge, Memoirs of the V Conference Uciencia, Firefox and Web development tool.} % Role
{Uciencia 2010} % Event
{} % Location
{2010} % Date(s)
{ % Description(s)
}

\cventry
{I Workshop systems information management of information and knowledge, Memoirs of the V Conference Uciencia, Creating themes in Drupal 6.} % Role
{Uciencia 2010} % Event
{} % Location
{2010} % Date(s)
{ % Description(s)
}

\cventry
{Digital Library: a complement to the system of university libraries, OAI-PMH, technological component for open access.} % Role
{Uciencia 2012} % Event
{} % Location
{2012} % Date(s)
{ % Description(s)
}

\cventry
{Creating themes in Drupal 6.} % Role
{The 9th week of FORDES technology (2009)} % Event
{} % Location
{2009} % Date(s)
{ % Description(s)
}

\cventry
{Theme in the management of educational institutions, reports of VII International Workshop of educational innovation XXI century.} % Role
{InnoEd`2013} % Event
{} % Location
{2013} % Date(s)
{ % Description(s)
}

\cventry
{The base level, UCI: Digital Library: a complement to the system of university libraries.} % Role
{20. University 2012 } % Event
{} % Location
{2011} % Date(s)
{ % Description(s)
}


\end{cventries}
